Spatial distribution of environmental DNA in a nearshore marine habitat

### 2017-01-11 Manuscript/v1.1_PeerJ/carkeek_grid.tex
respond to reviews

 \subsubsection*{(3) Richness declines and evenness increases with distance from shore}
We found that richness declined while evenness increased with distance from shore.
Such a pattern is consistent with many other ecosystems which show strong clines in diversity metrics over environmental gradients.
However, our study is novel in that it corroborates a cline well-known on macroscales for macrobiota on a much smaller spatial scale for microscopic animals, suggesting that there may be a self-similarity across scales in diversity patterning \citep{Levin1992}.
The coastal ocean is a highly productive and diverse ecosystem, where biomass is concentrated most heavily along the bottom and shoreline \citep{Ray1988}.
Our
Intriguingly, the cline in diversity from inshore to offshore was not determined by shared changes in communities as one moved offshore; the classification analysis suggested a fair amount of differences among communities at a given offshore distance (Figure \ref{pam_in_space}).

>>>>

 \subsubsection*{(3) Richness declines and evenness increases with distance from shore}
We found that richness declined while evenness increased with distance from shore.
Such a pattern is consistent with many other ecosystems which show strong clines in diversity metrics over environmental gradients.
However, our study is novel in that it corroborates a cline well-known on macroscales for macrobiota on a much smaller spatial scale for microscopic animals, suggesting that there may be a self-similarity across scales in diversity patterning \citep{Levin1992}.
The coastal ocean is a highly productive and diverse ecosystem, where biomass is concentrated most heavily along the bottom and shoreline \citep{Ray1988}.
This differential in biomass concentration from the shoreline to open waters may contribute to the opposing trends we detected.
Where particles (organisms, tissues, and cells) are sparse, fewer would be collected per sample of constant volume, thus decreasing the probability of drawing as many types (richness) and increasing the probability that any two particles originate from the same type (evenness).
Intriguingly, the cline in diversity from inshore to offshore was not determined by shared changes in communities as one moved offshore; the classification analysis suggested a fair amount of differences among communities at a given offshore distance (Figure \ref{pam_in_space}).
